--- 
title: "Super links"
author: "Lingyun Zhang"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
link-citations: yes
links-as-notes: true
colorlinks: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preface {-}

This book collects super links. More will come ...

# My books

1. https://zhanglynz.github.io/python_ex/
1. https://weirdr.netlify.app/
1. https://notesrpackages.netlify.app/
1. https://adrnotes.netlify.app/
1. https://zhanglynz.github.io/python_book/
1. https://zhanglynz.github.io/readingR4DS/
1. https://zhanglynz.github.io/djr_book/
1. https://zhanglynz.github.io/notesOnGit/
1. https://zhanglynz.github.io/learning_bayesian_stats/
1. https://zhanglynz.github.io/work_out_data/
1. https://zhanglynz.github.io/learn_R_in_x_lessons/
1. https://zhanglynz.github.io/r_book_17_howtos/
1. https://zhanglynz.github.io/practicalR/
1. https://zhanglynz.github.io/sampling_b/
1. https://zhanglynz.github.io/understanding_sampling/
1. https://zhanglynz.github.io/tip_collection/
1. https://zhanglynz.github.io/my_lessons_in_using_R/
1. https://zhanglynz.github.io/elementary-maths/
1. https://zhanglynz.github.io/mathematical-experiments/
1. https://zhanglynz.github.io/algebra_notes/
<!-- 1. https://zhanglynz.github.io/LearnGit/ -->
1. https://zhanglynz.github.io/dealing_with_strings/
1. https://zhanglynz.github.io/dealing_with_big_data/
1. https://zhanglynz.github.io/rare_r_functions/
1. https://zhanglynz.github.io/python_notes/

# My homepage/blog

https://larryzhangnz.netlify.app/

# Videos

## Learn how to learn 

**URL**: https://www.youtube.com/watch?v=vd2dtkMINIw

Key ideas: focused mode vs. diffusion mode; sleep is important; chunks; recall; practice and repetition; brain muscles

Comments: It's great. Although, some parts may be kind of boring but I can and---I believe---you can as well get something very useful from watching the video. A tip: the QA part is wonderful.

## Learn coding

**URL**: https://www.youtube.com/freecodecamp

## Peng's Posdcast

**URL**: https://nssdeviations.com/

# Forum and Blog Sites

1. Quarto: https://quarto.org/
1. coding club: https://www.hertiecodingclub.com/
1. Real World Data Science: https://realworlddatascience.net/
1. captial of statistics: https://cosx.org/
1. a blog: https://ivelasq.rbind.io/
1. tidyverse: https://www.tidyverse.org/
1. a blog: https://www.mm218.dev/blog
1. a blog: https://rfortherestofus.com/blog


# Books

## A source

1. https://www.linuxlinks.com/best-free-open-source-software-documentation/


## R related

1. EDA With R: https://bookdown.org/rdpeng/exdata/

1. telling story with data: https://tellingstorieswithdata.com/

1. Tidyverse Skills for Data Science: https://jhudatascience.org/tidyversecourse/

1. R Without Statistics
https://book.rwithoutstatistics.com/

1. Git doc, **URL:** https://docs.github.com/en/get-started/quickstart/github-flow

1. Git quick guide, **URL:** https://rogerdudler.github.io/git-guide/

1. Git hands-on session within RStudio, **URL:** https://inbo.github.io/git-course/course_rstudio.html

1. https://github.com/git-guides

1. Package development: https://mirai-solutions.ch/techguides/index.html

1. https://docs.posit.co/ide/user/

1. Package doc: https://rdrr.io/ 


## Python

1. **URL:** https://automatetheboringstuff.com/

## Java

1. https://math.hws.edu/javanotes/

1. https://greenteapress.com/thinkjava7/html/

## Java script

1. https://eloquentjavascript.net/

## Bayes

1. **URL:** https://www.bayesrulesbook.com/chapter-1.html

# Articles

## R related 

1. Top 7 Best R Shiny Books, **URL:** https://www.r-bloggers.com/2022/01/top-7-best-r-shiny-books-and-courses-that-are-completely-free/

    - Mastering Shiny by Hadley Wickham
    - Outstanding User Interfaces With Shiny by David Granjon
    - Engineering Production-Grade Shiny Apps by Colin Fay
    - The Shiny AWS Book by Matt Dancho
    - JavaScript 4 Shiny by Colin Fay
    - A gRadual intRoduction to Shiny by Ted Laderas
    - How to Start Shiny by RStudio
    
1. Rmarkdown tips, such as using tabs **URL:** https://www.r-bloggers.com/2022/09/r-markdown-lesser-known-tips-tricks-4-looks-better-works-better/

1. Shiny dashboard: https://www.r-bloggers.com/2023/03/how-to-customise-the-style-of-your-shinydashboard-shiny-app/

1. Stringr vss base R: https://stringr.tidyverse.org/articles/from-base.html

1. https://stackoverflow.com/questions/35852722/how-do-you-read-a-password-protected-excel-file-into-r

1. https://support.posit.co/hc/en-us/articles/219949047-Installing-older-versions-of-packages

1. https://cran.r-project.org/web/packages/janitor/vignettes/janitor.html

## SQL

1. duckdb: https://duckdb.org/

1. https://www.r-bloggers.com/2022/04/iterating-over-multiple-database-tables-with-r/ 
Iterating over multiple database tables with R

1. https://www.johnmackintosh.net/blog/2022-04-06-sql-schema-query/

## Geo

1. https://rapidlasso.com/2019/05/06/how-many-decimal-digits-for-storing-longitude-latitude/#:~:text=Longitude%20and%20latitude%20coordinates%20are,right%20of%20the%20decimal%20points

1. https://www.r-bloggers.com/2023/03/how-to-geocode-in-r-for-free/

# Tools

1. https://quarto.org/
Quarto is an open-source scientific and technical publishing system built on Pandoc

1. https://www.rscreencasts.com/ 
Awesome data analysis screencasts from a top Data Scientist

1. https://www.r-bloggers.com/2022/05/software-development-resources-for-data-scientists/
Software Development Resources for Data Scientists

# My workflows

## Book project

R markdown book:

1. create a repo at Github
1. create a project at RStudio
1. run BookStarter::start_book()
1. edit index.Rmd
1. edit _bookdown.yml
1. chapters 1, 2, 3, ....

Quarto book:

1. create a repo at Github
1. create a project at RStudio
1. run BookStarter::q_start_book()
1. edit index.Rmd
1. edit _quarto.yml
1. chapters 1, 2, 3, ....

Quarto book published on netlify:

1. Create a repo at Gitlab
1. In RStudio: 
    - File > New Project > New Directory > Quarto Book ...; 
    - Change `index.qmd`, `_quarto.yml`
    - Change `.gitignore` file (add `.quarto/` and `.Rproj.user/` into the file)
    - Use terminal: 
        - `git remote add origin https://...`
        - `git add .`
        - `git commit -m "a commit"`
        - `git push -u origin main`
- Log into netlify and do the stetting up
- Update `superlinks` book
    

In VS code

1. Click top left icon >> View >> Command Palette >> Quarto: Create Project >> Book Project >> ...
1. Change _quarto.yml
1. Work on .qmd files
1. If in _quarto.yml, "output-dir: docs", then create "docs" folder
1. To render and preview
    - open a new terminal, and type "quarto render"
    - type "quarto preview"
1. Create an EMPTY repo at Github
1. Do local setups
    - git init
    - git remote add origin https://...
    - git add .
    - git commit -m "initial commit"
  	- git push -u origin main
1. Github setups
    - Settings >> Pages >> ...


## My blog

1. run ./R/to_have_a_new_post.R
1. edit index.Rmarkdown: always adding "math: true" in the yaml header; always using ````<p>$$math formula$$</p>```` 
1. knit index.Rmarkdown
1. manually dealing with in-line math formulas---using Find and Replace
1. commit to Github	

## Paper in Tex

1. create a repo at Github
1. create a project at RStudio
1. run BookStarter::start_tex(tex_file_name = "my_paper.tex")

## Creating R package

```{r, eval=FALSE}
library(devtools)
create_package("~/path/to/regexcite") # only use once; to scaffold a new R package

library(devtools)
use_r("func_name") + (in the source editor and put the cursor somewhere in the strsplit1() function definition. Now do Code > Insert roxygen skeleton.)
load_all()
check()
Edit DESCRIPTION
use_mit_license() # only use once
document()
check() # again
install()
use_testthat() # only use it once
use_test("strsplit1")
use_package("some_a_package") # dependence

Gitlab # Git the project; push to Gitlab
# push an existing repository from the command line (Gitbash)
cd existing_folder
git init --initial-branch=main
git remote add origin git@gitlab.com:larry_zhang_nz/testpkg05nov2023.git
git add .
git commit -m "Initial commit"
git push --set-upstream origin main

use_readme_rmd() # only use it once
check() # again 
install()
```

# Useful Git commands

Git is a powerful version control system with a wide range of commands. Here are some of the most useful and commonly used Git commands:

## Basic Commands

1. **git init**  
   Initializes a new Git repository in the current directory.

2. **git clone [repository_url]**  
   Clones a remote repository to your local machine.

3. **git status**  
   Shows the status of your working directory, including tracked, untracked, and modified files.

4. **git add [file]**  
   Adds a file to the staging area. Use `git add .` to add all changes.

5. **git commit -m "[commit_message]"**  
   Commits the staged changes with a descriptive message.

6. **git push [remote] [branch]**  
   Pushes your local commits to a remote repository. Example: `git push origin main`.

7. **git pull [remote] [branch]**  
   Fetches changes from a remote repository and merges them into your current branch.

8. **git fetch [remote]**  
   Downloads changes from a remote repository but does not merge them.

---

## Branching and Merging

9. **git branch**  
   Lists all local branches. Use `-r` for remote branches or `-a` for all branches.

10. **git branch [branch_name]**  
    Creates a new branch.

11. **git checkout [branch_name]**  
    Switches to the specified branch.

12. **git checkout -b [new_branch_name]**  
    Creates and switches to a new branch.

13. **git merge [branch_name]**  
    Merges the specified branch into the current branch.

14. **git rebase [branch_name]**  
    Reapplies commits from the current branch onto the specified branch.

---

## Viewing History and Changes

15. **git log**  
    Displays the commit history. Use `--oneline` for a compact view.

16. **git diff**  
    Shows differences between the working directory and the staging area.

17. **git diff [commit1] [commit2]**  
    Shows differences between two commits.

18. **git show [commit]**  
    Displays details about a specific commit.

---

### Undoing Changes
19. **git reset [file]**  
    Unstages a file while keeping changes in the working directory.

20. **git reset --hard [commit]**  
    Resets the working directory and staging area to a specific commit (use with caution).

21. **git revert [commit]**  
    Creates a new commit that undoes the changes of a previous commit.

22. **git checkout -- [file]**  
    Discards changes in the working directory for a specific file.

---

## Remote Repositories

23. **git remote -v**  
    Lists all remote repositories.

24. **git remote add [name] [url]**  
    Adds a new remote repository.

25. **git remote remove [name]**  
    Removes a remote repository.

26. **git push --set-upstream [remote] [branch]**  
    Sets the upstream branch for the current local branch.

---

## Stashing

27. **git stash**  
    Temporarily saves changes in the working directory.

28. **git stash pop**  
    Applies the most recently stashed changes and removes them from the stash.

29. **git stash list**  
    Lists all stashed changes.

30. **git stash apply**  
    Applies stashed changes without removing them from the stash.

---

## Tagging

31. **git tag [tag_name]**  
    Creates a lightweight tag for the current commit.

32. **git tag -a [tag_name] -m "[message]"**  
    Creates an annotated tag with a message.

33. **git push [remote] --tags**  
    Pushes tags to a remote repository.

---

## Advanced Commands

34. **git bisect**  
    Helps find the commit that introduced a bug using binary search.

35. **git cherry-pick [commit]**  
    Applies a specific commit from one branch to another.

36. **git reflog**  
    Shows a log of all reference changes, useful for recovering lost commits.

37. **git clean -fd**  
    Removes untracked files and directories from the working directory.

---

